---
title: "R Shiny Presentation"
author: "Lauren Yabuki"
date: "10/11/2020"
output: ioslides_presentation
runtime: shiny
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

## Shiny Presentation

This R Markdown presentation is made interactive using Shiny according to Coursera assignment Shiny Application and Reproducible Pitch. 
The data give the maximum daily temperature in degrees Fahrenheit at La Guardia Airpor from the data package airquality.

## Course Project: Shiny Application

1. Write a shiny application with associated supporting documentation. The documentation should be thought of as whatever a user will need to get started using your application.
2. Deploy the application on Rstudio's shiny server
3. Share the application link by pasting it into the provided text box
4. Share your server.R and ui.R code on github

## Course Project: Reproducible Pitch Presentation

1. 5 slides to pitch our idea done in Slidify or Rstudio Presenter
2. Your presentation pushed to github or Rpubs
3. A link to your github or Rpubs presentation pasted into the provided text box: 
https://github.com/laurenyabuki/Shiny-Application-and-Reproducible-Pitch.git
https://laurenyabuki.shinyapps.io/Coursera_Project_Shiny_application/?_ga=2.176921644.8093120.1605043910-289867867.1605043910

## Interactive Plot

```{r airquality}
library(shiny)
data(airquality)

# Define UI for app that draws a histogram ----
ui <- fluidPage(
  
  # App title ----
  titlePanel("Maximum daily temperature in degrees Fahrenheit at La Guardia Airport"),
  
  # Sidebar layout with input and output definitions ----
  sidebarLayout(
    
    # Sidebar panel for inputs ----
    sidebarPanel(
      
      # Input: Slider for the number of bins ----
      sliderInput(inputId = "bins",
                  label = "Number of bins:",
                  min = 50,
                  max = 100,
                  value = 20)
      
    ),
    
    # Main panel for displaying outputs ----
    mainPanel(
      
      # Output: Histogram ----
      plotOutput(outputId = "distPlot")
      
    )
  )
)
inputPanel(
  selectInput("n_breaks", label = "Number of bins:",
              choices = c(10, 20, 35, 50), selected = 20),
  
  sliderInput("bw_adjust", label = "Bandwidth adjustment:",
              min = 0.2, max = 2, value = 1, step = 0.2)
)
```

```{r}
# Define server logic required to draw a histogram ----
server <- function(input, output) {
  

  output$distPlot <- renderPlot({
    
    x    <- airquality$Temp
    x    <- na.omit(x)
    bins <- seq(min(x), max(x), length.out = input$bins + 1)
    
    hist(x, breaks = bins, col = "#75AADB", border = "black",
         xlab = "Temperature",
         main = "Histogram of Maximum Temperature")
    
  })
}
# Create Shiny app ----
shinyApp(ui = ui, server = server)
```



